Design and Implementation of\\Anglican Probabilistic Programming Language

### 2016-09-01 slides/slides.tex
added worksheet

\begin{frame}{Language}
\end{frame}

\begin{frame}{Macro-based compilation}
\end{frame}

>>>>

\begin{frame}{Anglican and Clojure}
    On language on top of (or besides) another:
    \begin{itemize}
        \item Interpeter.
        \item Source-to-source compiler.
        \item Integrated language. $\checkmark$
    \end{itemize}
    \pause
    \bigskip
    Integrated language
    \begin{itemize}
        \item either extends the syntax of the host language;
        \item or changes the semantics of the host language
            constructs $\checkmark$.
    \end{itemize}
    \pause
    \bigskip
    Anglican is 
    \begin{itemize}
        \item Integrated with Clojure.
        \item Shares syntax.
        \item Alters operational semantics.
    \end{itemize}
\end{frame}

\begin{frame}{Anglican}
    A subset of Clojure, wrapped inside \texttt{defquery}:
    \begin{itemize}
        \item \texttt{if}, \texttt{when}, \texttt{cond},
            \texttt{case}, \texttt{let}, \texttt{and}, \texttt{or},
            \texttt{fn}. 
        \item Vector destructuring in bindings of \texttt{let} and \texttt{fn}.
        \item Compound literals for vectors, hash maps, and sets.
        \item \texttt{loop}/\texttt{recur} --- a convenience.
    \end{itemize}
    \bigskip
    Core library:
    \begin{itemize}
        \item All of Clojure core library, except for
            higher-order functions.
        \item  \texttt{map}, \texttt{reduce},
\texttt{filter}, \texttt{some}, \texttt{repeatedly},
\texttt{comp}, \texttt{partial}.
    \end{itemize}
    \bigskip
    Any Clojure function can be called from Anglican.
\end{frame}

\begin{frame}[fragile]{Macro-based compilation}
    Anglican code macro-compiled into Clojure:
    \begin{minipage}{0.48\textwidth}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(loop [data data]
  (if (seq data)
    (let [[x & data] data]
      (observe (gamma a b) x)
      (recur data))
    (predict :a a)))
\end{minted}
    \end{minipage}
    \begin{minipage}{0.44\textwidth}
    \vspace{2em}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(fn loop [C23151 state data]
   (if (seq data)
     (let [[x & data] data]
       (->observe 'O23153 (gamma a b) x
         (fn do23152 [_ state]
           (loop C23151 state data))
         state))
     (fn []
       (C23151
         nil
         (add-predict state :a a)))))
\end{minted}
    \end{minipage}
\end{frame}
